Data Specialization for a Staged Lambda Calculus

### 2014-11-06 paper/splitting.tex
setting up intro to masking definitions

Intuitively for splitting TO MATCH THIS THING ABOVE.  It needs to match the 3, and the resumer should reduce to the same value as the reified partial value.

@@

\ur{The following paragraph makes no sense to me, especially because
  it does not match Figure 11.  AS far as I can see Figure 11 does not
talk about masking but value splitting.}
We formalize this notion via two \emph{masking} functions (\ref{fig:valMask}),
$\masko{\cdot}$ and $\maskt{\cdot}$, which expose only the relevant structure of
a partial value at each stage, essentially by replacing all stage \bbone\
(resp., \bbtwo) components of a partial value by \texttt{()}. The first result
of splitting must then compute the \bbone-mask of the partial value, and the
second result the \bbtwo-mask.

>>>>

Note that this result carries information at {\em both} stages: 
at stage~\bbone\ it carries the value 3, and at stage~\bbtwo\ it carries the code $\letin \yhat {\mathtt{7+5}} \yhat$.

But the whole point of splitting is that its results (and their evaluated forms) are monostage.
Ergo, if we intend to compare the results of evaluation to the those of splitting, 
then we'll need some mechanism to project from the residual table and partial value only the parts that are relevant at a particular stage.

% Intuitively for splitting TO MATCH THIS THING ABOVE.  It needs to match the 3, and the resumer should reduce to the same value as the reified partial value.
To this end, we introduce two {\em masking} functions...

@@

We formalize this notion via two \emph{masking} functions (\ref{fig:valMask}),
$\masko{\cdot}$ and $\maskt{\cdot}$, which expose only the relevant structure of
a partial value at each stage, essentially by replacing all stage \bbone\
(resp., \bbtwo) components of a partial value by \texttt{()}. The first result
of splitting must then compute the \bbone-mask of the partial value, and the
second result the \bbtwo-mask.
